---
title: "TUTORIAL 5"
author: "Najla"
date: "2024-04-21"
output:
  word_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(qcc)
library(dplyr)
```

Table 7E.10
```{r}
plate_number <- c(1:25)
number_nonconform <- c(1,0,4,3,1,2,5,0,2,1,1,0,8,0,2,1,3,5,4,6,3,1,0,2,4)
plates <- data.frame(plate_number, number_nonconform)
```

exercise 7.36
```{r}
np <- mean(number_nonconform)
np
npq <- sd(number_nonconform)
npq

np_ucl <- np + 3*sqrt(npq)
np_ucl

np_cl <- np
np_cl

np_lcl <- np - 3*sqrt(npq)
np_lcl=0

qcc(data=number_nonconform, type="np", sizes=1, stdev=1.455665, limits=c(np_lcl,np_ucl), plot=TRUE)
```

The np Chart shows one subgroup are out of upper control limit. So, we may conclude the process is out of control.

Table 7E.11
```{r}
Day <- c(1:20)
number_rolls_produced <- c(18,18,24,22,22,22,20,20,20,20,18,18,18,20,20,20,24,24,22,21)
total_imperfections <- c(12,14,20,18,15,12,11,15,12,10,18,14,9,10,14,13,16,18,20,17)
paper <- data.frame(Day, number_rolls_produced, total_imperfections)
```

Exercise 7.37

```{r}
#variable u : 
paper1 <- paper %>% group_by(Day) %>% mutate(mean= total_imperfections/number_rolls_produced)
ubar <- mean(paper1$mean)
ubar

paper.ucl <- paper1 %>% group_by(Day) %>% mutate(ucl = ubar + 3*sqrt(ubar/number_rolls_produced))
paper.lcl <- paper.ucl %>% group_by(Day) %>% mutate(lcl = ubar - 3*sqrt(ubar/number_rolls_produced))
paper.lcl

qcc(data=paper1$mean, sizes=1, type="u", limits=c(paper.lcl$lcl,paper.ucl$ucl))
```

Exercise 7.38
```{r}
#averaged u : 
avg_n <- mean(number_rolls_produced)
avg_n

paper2 <- paper %>% group_by(Day) %>% mutate(mean= total_imperfections/avg_n)
ubar2 <- mean(paper2$mean)

avg.ucl <- ubar2 + 3*sqrt(ubar2/avg_n)
avg.ucl

avg.lcl <- ubar2 - 3*sqrt(ubar2/avg_n)
avg.lcl

qcc(data=paper2$mean, sizes=1, type="u", stdev=sqrt(ubar2/avg_n), limits=c(avg.lcl,avg.ucl))
```

The process seems to be in control.

Table 7E.13

```{r}
sample_number <- c(1:22)
number_nonconformities <- c(1,1,3,7,8,10,5,13,0,19,24,6,9,11,15,8,3,6,7,4,9,20)
telephone <- data.frame(sample_number, number_nonconformities)
```

Exercise 7.41
```{r}
cbar <- mean(number_nonconformities)
cbar

c_ucl <- cbar+ 3*sqrt(cbar)
c_ucl

c_lcl <- cbar- 3*sqrt(cbar)
c_lcl=0

qcc(data=number_nonconformities, type="c", sizes=1, stdev= sqrt(cbar), limits=c(c_lcl,c_ucl),plot=TRUE)
```

From the chart, we see that there are 3 subgroups, 10,11 22 are out of control limit. Hence, we may conclude that the process is out of control.
For the future production, we may identify the assingnable causes of the out control subgroups and produced a revised control limits by eliminating the assignable causes subgroups.

```{r}
nonconformities <- c(1,1,3,7,8,10,5,13,0,6,9,11,15,8,3,6,7,4,9)

cbar1 <- mean(nonconformities)
cbar1

c_ucl1 <- cbar1+ 3*sqrt(cbar1)
c_ucl1

c_lcl1 <- cbar1- 3*sqrt(cbar1)
c_lcl1=0

qcc(data=nonconformities, type="c", sizes=1, stdev= sqrt(cbar1), limits=c(c_lcl1,c_ucl1),plot=TRUE)
```

we see thats subgroups 13 is out of control, hence we need to eliminate subgropus 13.
```{r}
nonconformities1 <- c(1,1,3,7,8,10,5,13,0,6,9,11,8,3,6,7,4,9)
cbar2 <- mean(nonconformities1)
cbar2

c_ucl2 <- cbar2+ 3*sqrt(cbar2)
c_ucl2

c_lcl2 <- cbar2- 3*sqrt(cbar2)
c_lcl2=0

qcc(data=nonconformities1, type="c", sizes=1, stdev= sqrt(cbar2), limits=c(c_lcl2,c_ucl2),plot=TRUE)
```

Now, the process is in control.

EXERCISE 7.43

```{r}
#The new inspection unit is 2.5 of the old unit

# C CHART FOR TOTAL NUMBER OF NONCONFORMITIES IN NEW INSPECTION UNIT :  
new_cl <- cbar2*2.5
new_cl 

new_c_ucl <- new_cl + 3*sqrt(new_cl)
new_c_ucl

new_c_lcl <- new_cl - 3*sqrt(new_cl)
new_c_lcl

qcc(data=nonconformities1*2.5, type="c", sizes=1, stdev= sqrt(new_cl), limits=c(new_c_lcl,new_c_ucl),plot=TRUE)
```

b)
```{r}
xbar <- mean(nonconformities1)

#Average number of non-conformities per inspection unit,n
n=1000/2500
u_ubar <- xbar/n
u_ubar

#center line and control limits for u chart
center_line <- u_ubar
u_ucl <- u_ubar + 3*sqrt(u_ubar/0.4)
u_ucl
u_lcl <- u_ubar - 3*sqrt(u_ubar/0.4)
u_lcl=0

qcc(data=nonconformities1/n, type="u", sizes=1, stdev= sqrt(u_ubar), limits=c(u_lcl,u_ucl),plot=TRUE)
```